Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-05 paper.tex
unified model

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                    Challenges in Co-verification 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The verification of FW given in C/C++ together with the RTL given in a hardware
description language (HDL) such as Verilog/VHDL is a challenging task due to 
few reasons -- 1) the timing and semantic mismatch between the synchronous
clock-driven HW model and asynchronous event-driven SW model -- for example,
FW running on a processor could be much faster than the HW
model it interacts with, 2) lack of co-specification model that precisely
captures the design intent of the communication between HW and FW, 3) Large
number of interleavings between HW and FW threads, and 4) lack 
of automated formal tools that support co-designs implemented in C/C++ and 
Verilog/VHDL.   In this paper, we address some of these challenges to enable
seamless adoption of formal techniques in hardware/software co-verification.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                     Handling Semantic Gap  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Generating a unified FW-HW model for co-verification is a 
well-known phenomenon to handle the semantic mismatch between the 
HW~\footnote{Note that whenever we refer to ``hardware'' 
from this point onwards, we mean an RTL implementation 
and not a TLM.}  and FW models.  Most of the existing techniques 
in~\cite{fmsd02,emsoft07,fase10} for constructing a unified FW-HW model are not 
useful in practise for three reasons -- 1) use of abstract HW models 
instead of register-transfer level implementation, 2) the HW-FW model
construction is agnostic to the underlying reasoning engine, 3) does not
leverage the co-specification model, hence ineffective for practical
co-verification.  We will call the unified FW-HW model as \emph{co-verification model}.

@@

@@

\textbf{Co-design Property} We verify that the transmitted data is the same as the 
received data in the {\em loopback} mode.  To do so, we annotate the FW model 
with an assertion $assert()$, as shown in Figure~\ref{firmware}.  Note that the 
array containers $rx\_b$ and $tx\_b$ stores the data obtained through the $inb$
and $outb$ function calls which directly read from and write to the UART IP ports
respectively. \rmcmt{more on co-specification PSL}. 
\[
  for(i=0; i<=N; i++) 
   \quad assert(rx\_b[i] == tx\_b[i]);
\]
%
\section{Scenario and Transaction}
%
We formally describe the notion of \emph{transaction} and \emph{scenario} with the
help of our working example. \\
%
\begin{figure}[t]
\scriptsize
\begin{tabular}{|l|l|}
\hline
Wishbone Interface & Main Module \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
typedef unsigned char u8;
unsigned char inb 
 (unsigned long port) {
  return wb_read(port);
}
void outb (u8 value, 
 unsigned long port) {
  wb_write(port, value);
}
void wb_reset(void) {
 rst_i = 1;
 set_inputs();
 next_timeframe();
 rst_i = 0;
 stb_i = 0; 
 cyc_i = 0;
}
void wb_idle() {
 set_inputs();
 next_timeframe();
}
void wb_write(_u32 addr, 
     _u8 b) {
 adr_i = addr;
 dat_i = b;
 we_i = 1;
 cyc_i = 1;
 stb_i = 1;
 set_inputs();
 next_timeframe();
 we_i = 0;
 cyc_i = 0;
 stb_i = 0;
}
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
int main() {
wb_reset();
wb_idle();
// Configure the uart
outb (0x13, UART_MC);  
outb (0x80, UART_CM3);
outb (0x00, UART_CM2);
outb (0x00, UART_CM1);
outb (0x00, UART_CR);  
outb (0x03, UART_IE); 
char tx_b[] = "Hello world";
_u8 status = 0;
char rx_b[100];
int i=0,c=0,d=0;
// data transfer in loopback
for (i=0; i<1990; i++){
if (irq_o){
 status=inb(UART_IS)&0x0c;
 if(istatus==0x0c){
 //it was a tx_empty interrupt
 outb(*(tx_b+c),UART_TR); c++;
 }
 else{ //status==0x04
 //it was an rx_data interrupt
  rx_b[d] = inb(UART_TR); d++;
 }
}else {
 // no interrupt. 
 wb_idle();
 wb_idle();
 }
}
// property
for(i=0; i<=10; i++)
 assert(rx_b[i] == tx_b[i]);
}
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{Firmware model of UART IP}
\label{firmware} 
\end{figure}
%

@@

attempt that demonstrate the efficacy of such translation in the context of 

@@

Figure~\ref{fig:interleaving1} illustrates the producer-consumer relationship 
in UART IP. The FW CFG is shown in the left and the 
HW RTL code snippet is shown in the right. We abuse notations and 
represent $\mathcal{HT}$ in the form of RTL and $\mathcal{FT}$ as CFG
for our illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
status signal, $irq\_o$, which is read by $\mathcal{FT}$ in state $s_1$. 
The signal $irq\_o$ is  triggered when transmitter buffer is 
{\em EMPTY} or receiver buffer is {\em FULL}. 
$\mathcal{HT}$ also produces interrupt status by writing to the 
memory mapped register, $UART\_IS$, which is consumed by 
$\mathcal{FT}$ in state $s_2$.  In another interaction, $\mathcal{HT}$
sends a data-packet to $UART\_TR$ which is consumed by $\mathcal{FT}$ in state $s_7$.
Similarly, $\mathcal{FT}$ is the producer of $data$, $(outb(data,UART\_TR))$, 
in state $s_6$ which is consumed by $\mathcal{HT}$.  
%
\begin{figure}[t]
\scalebox{.55}{\import{figures/}{interleaving.pspdftex}}
\caption{Producer Consumer Interactions Pattern
\label{fig:interleaving1}}
\end{figure}
%
Table~\ref{transaction} shows the FW transactions $(\mathcal{FT})$ and its 
interacting HW transactions $(\mathcal{HT})$ from Figure~\ref{fig:interleaving1}. 
The description above the arrows 
in column 1 shows the events in $\mathcal{FT}$ and the letter below the
arrows denotes the event type, producer $(\mathcal{P})$ or consumer 
$(\mathcal{C})$. Arrows with empty description below denotes reading of interface
variables or local variables in $\mathcal{FT}$.  Arrows with no description
simply denotes control-flow with no events.  The entires in the right column of
Table~\ref{transaction} shows the corresponding transaction in HW modules. We
simply denote a transaction in HW module with the name of the module,
transmitter module in UART ($uart\_tx$), receiver module in UART ($uart\_rx$), or
the top UART module ($uart\_top$).
%
\begin{table}
\begin{center}
{
 \scriptsize
\begin{tabular}{|c|c|c|}
\hline
  Firmware & Hardware  \\
  Transaction ($\mathcal{ST}$) & Transaction ($\mathcal{HT}$) \\ 
\cline{1-2}
   $s_1 \xrightarrow[]{irq_o} s_2 \xrightarrow[\mathcal{C}]{inb()} s_4
   \xrightarrow[]{status == 0x0c} s_6 \xrightarrow[\mathcal{P}]{outb()} s_9 \rightarrow
   s_{11} \rightarrow s_{12}$  & $s_2 \xrightarrow[\mathcal{C}]{inb()} s_4\;\; uart\_{rx}$
   \\ 
   & $s_6 \xrightarrow[]{outb()} s_9\;\; uart\_{tx}$ \\  \hline

@@

\textbf{Step 3: Co-verification Model}
An unified co-verification model is constructed through appropriate composition of 
FW and its interacting HW threads.  This is done by instrumenting the 
software netlist model of HW RTL inside the FW thread at every invocation 
of the interface functions.  This leads to a single-threaded sequential
co-verification model in C.  
%
We now formally define a our co-verification model, denoted by 
$\mathcal{M}_{seq}$.\rmcmt{refer moduleName} as software netlist.
%
\[ 
\begin{array}[t]{@{}lll}
  \mathcal{M}_{seq} & {:}{:}{=} & \mathit{Procedure} \\
\mathit{Procedure} & {:}{:}{=} & \mathit{Statement} \mid \mathit{Procedure} \\
\mathit{Statement} & {:}{:}{=} & CStatement \mid \mathit{moduleName(Var_1,\dots,Var_n)} \\
\mathit{CStatement} & {:}{:}{=} & x {:}{=} exp \mid \mathit{ITE}(b, s_1,s_2) \mid \mathit{s_1;s_2} \mid loop\{s\} \\ 
\end{array}
\]
%
Consider sets of expressions $Exp$ and Boolean expressions $BExp$ 
over variables $Var$ of $\mathcal{M}_{seq}$ such that $(exp \in Exp)$ and 
$(b \in BExp)$. A $\mathit{CStatement}$ is an assignment,
conditional, sequential concatenation or a loop.
$\mathit{moduleName(Var_1,\dots,Var_n)}$ invokes the top level 
procedure of the $\mathcal{SN}$. Recall that $\mathcal{SN}$ is a
software netlist representation of HW RTL models.
The interface variables $\{Var\_1,\dots,Var\_n\}$ 
(input, output and inout ports) are declared inside the 
FW to communicate with $\mathcal{SN}$. \rmcmt{explain instrumentation with
diagram} \\ 
%

\textbf{Step 4: Property Driven Slicing of Co-verification Model}
A property-driven slicing is performed on the unified model, $\mathcal{M}_{seq}$.  
This step is purely syntactic, meaning that we perform a backward dependency 
analysis starting from the property which only preserve those 
program fragments that are relevant to a given property. The sliced program 
is then passed to the symbolic execution engine for path-based exploration. \\
%
%=======================================================================================
%\subsection{\verifox: Path-wise Symbolic Execution Tool} 
%=======================================================================================
\input{verifox}
%
\subsection{Approach 2: Monolithic Co-verification Technique}
%
\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.6]{figures/traditional_flow.pdf}
\caption{Monolithic HW/SW Co-verification Flow}
\label{fig:conventional}
\end{center}
\end{figure}
%
Figure~\ref{fig:conventional} illustrates the conventional approach to HW/SW
co-veri\-fi\-cation, as implemented in the state-of-the-art co-verification
tool, \hwcbmcv~\cite{CKY03,vlsid13}.  \hwcbmcv is the only open-source
formal co-verification tool that supports Verilog RTL (System Verilog 2009
standard) and C/C++ firmware.  In contrast to our proposed approach,
\hwcbmcv maintains two separate flows for HW and FW.  The top flow in
Figure~\ref{fig:conventional} uses synthesis to obtain either a bit-level or
a word-level netlist from Verilog RTL.  The bottom flow illustrates the
translation of the C program into static single assignment (SSA) form. 
These two flows meet only at the solver.  Thus, \hwcbmcv generates a
monolithic formula from the C and RTL description, which is then checked
with SAT/SMT solvers.  \hwcbmcv provides specific handshake primitives such
as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
\rmcmt{
To this end, \hwcbmcv constructs a co-verification model through 
in tandem symbolic execution of the HW and FW models.  A bit-level 
netlist representation in And Inverter Graph (AIG) format or word-level netlist in
format similar to SMT-LIB standards is synthesized from a HW Register Transfer 
Level (RTL) implementation. Similarly, the SW, given in C, is automatically 
translated into a Static Single Assignment (SSA) form.  A monolithic verification 
condition is generated from these two models which is then solved using a 
}
%
\Omit{
The hardware and firmware run independently of each other. 
The communication between them takes place through these function calls. 
}
%===============================================================================
\section{Property Specification for Co-verification}
%===============================================================================
Lack of support for property specification in a HW/SW co-design is one of the
stumbling blocks for the application of formal techniques in co-verification.  
In this paper, we express a co-design property in C 
with the support of special primitive, called {\em next\_timeframe()}, 
that can express temporal correlation between HW and FW events. 
In this paper, we classify co-design properties into two 
classes -- {\em transaction-level} property and {\em component-level} property.
%-------------------------------------------------------------------------------
\subsection{Transaction-level Property}
%-------------------------------------------------------------------------------
A {\em Transaction-level} property ($\psi_{t}$) formally captures the 
design intent of the interaction between a $\mathcal{ST}$ and $\mathcal{HT}$, 
that is, it is defined at the transaction boundaries.  
Recall that a $\mathcal{ST}$ is a service in response to some external environment 
or HW interrupts (for example acknowledgement or exceptions). Similarly, 
$\mathcal{HT}$ is a finite-length service in response to some SW events or 
other HW events.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                    Challenges in Co-verification 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The verification of FW given in C/C++ together with the RTL given in a hardware
description language (HDL) such as Verilog/VHDL is a challenging task due to 
few reasons -- 1) the timing and semantic mismatch between the synchronous
clock-driven HW model and asynchronous event-driven SW model -- for example,
FW running on a processor could be much faster than the HW
model it interacts with, 2) lack of support for property specification in 
HW/FW co-designs that can precisely capture the design intent of the 
communication between HW and FW, 3) Large
number of interleavings between HW and FW threads, and 4) lack 
of automated formal tools that support co-designs implemented in C/C++ and 
Verilog/VHDL.   In this paper, we address some of these challenges to enable
seamless adoption of formal techniques in hardware/software co-verification.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %                     Handling Semantic Gap  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Generating a unified FW-HW model for co-verification is a 
well-known phenomenon to handle the semantic mismatch between the 
HW~\footnote{Note that whenever we refer to ``hardware'' 
from this point onwards, we mean an RTL implementation 
and not a TLM.}  and FW models.  Most of the existing techniques 
in~\cite{fmsd02,emsoft07,fase10} for constructing a unified FW-HW model are not 
useful in practise for three reasons -- 1) use of abstract HW models 
instead of register-transfer level implementation, 2) the HW-FW model
construction is agnostic to the underlying reasoning engine, and 3) 
does not leverage the property specification over HW-FW boundary, hence 
ineffective for practical co-verification.  We will call the unified FW-HW 
model as \emph{co-verification model}.

@@

\textbf{Interface functions} The \emph{interface functions} are lowest level of 
implementation in a FW model that directly read from or write to the HW ports. 
For example, the interface functions in figure~\ref{firmware} are the $wb$ class
of functions that directly wiggles the input/output ports of UART HW.

@@

\textbf{Co-design Property} We verify that the transmitted data is the same as the 
received data in the {\em loopback} mode.  To do so, we annotate the FW model 
with an assertion $assert()$, as shown in Figure~\ref{firmware}.  Note that the 
array containers $rx\_b$ and $tx\_b$ stores the data obtained through the $inb$
and $outb$ function calls which directly read from and write to the UART IP ports
respectively. Section~\ref{property} describes the property specification in
HW-FW co-designs in more details. 
\[
  for(i=0; i<=N; i++) 
   \quad assert(rx\_b[i] == tx\_b[i]);
\]
%
\section{Scenario and Transaction}
%
We formally describe the notion of \emph{transaction} and \emph{scenario} with the
help of our working example. \\
%
\begin{figure}[t]
\scriptsize
\begin{tabular}{|l|l|}
\hline
Wishbone Interface & Main Module \\
\hline
\begin{lstlisting}[mathescape=true,language=C]
typedef unsigned char u8;
unsigned char inb 
 (unsigned long port) {
  return wb_read(port);
}
void outb (u8 value, 
 unsigned long port) {
  wb_write(port, value);
}
void wb_reset(void) {
 rst_i = 1;
 set_inputs();
 next_timeframe();
 rst_i = 0;
 stb_i = 0; 
 cyc_i = 0;
}
void wb_idle() {
 set_inputs();
 next_timeframe();
}
void wb_write(_u32 addr, 
     _u8 b) {
 adr_i = addr;
 dat_i = b;
 we_i = 1;
 cyc_i = 1;
 stb_i = 1;
 set_inputs();
 next_timeframe();
 we_i = 0;
 cyc_i = 0;
 stb_i = 0;
}
\end{lstlisting}
&
\begin{lstlisting}[mathescape=true,language=C]
int main() {
wb_reset();
wb_idle();
// Configure the uart
outb (0x13, UART_MC);  
outb (0x80, UART_CM3);
outb (0x00, UART_CM2);
outb (0x00, UART_CM1);
outb (0x00, UART_CR);  
outb (0x03, UART_IE); 
char tx_b[] = "Hello world";
_u8 status = 0;
char rx_b[100];
int i=0,c=0,d=0;
// data transfer in loopback
for (i=0; i<1990; i++){
if (irq_o){
 status=inb(UART_IS)&0x0c;
 if(istatus==0x0c){
 //it was a tx_empty interrupt
 outb(*(tx_b+c),UART_TR); c++;
 }
 else{ //status==0x04
 //it was an rx_data interrupt
  rx_b[d] = inb(UART_TR); d++;
 }
}else {
 // no interrupt. 
 wb_idle();
 wb_idle();
 }
}
// property
for(i=0; i<=10; i++)
 assert(rx_b[i] == tx_b[i]);
}
\end{lstlisting}
\\
\hline
\end{tabular}
\caption{Firmware model of UART IP}
\label{firmware} 
\end{figure}
%

@@

attempt to demonstrate the efficacy of such translation in the context of 

@@

Figure~\ref{fig:interleaving1} illustrates the producer-consumer relationship 
in UART IP. The FW CFG is shown in the left and the 
HW RTL code snippet is shown in the right. We abuse notations and 
represent $\mathcal{HT}$ in the form of RTL and $\mathcal{FT}$ as CFG
for our illustration purpose. Here, $\mathcal{HT}$ is the producer of interrupt 
status signal, $irq\_o$, which is read by $\mathcal{FT}$ in state $s_1$. 
The signal $irq\_o$ is  triggered when transmitter buffer is 
{\em EMPTY} or receiver buffer is {\em FULL}. 
$\mathcal{HT}$ also produces interrupt status by writing to the 
memory mapped register, $UART\_IS$, which is consumed by 
$\mathcal{FT}$ in state $s_2$.  In another interaction, $\mathcal{HT}$
sends a data-packet to $UART\_TR$ which is consumed by $\mathcal{FT}$ in state $s_7$.
Similarly, $\mathcal{FT}$ is the producer of $data$, $(outb(data,UART\_TR))$, 
in state $s_6$ which is consumed by $\mathcal{HT}$.  
%
\begin{figure}[t]
\scalebox{.55}{\import{figures/}{interleaving.pspdftex}}
\caption{Producer Consumer Interactions Pattern
\label{fig:interleaving1}}
\end{figure}
%
Table~\ref{transaction} shows the FW transactions $(\mathcal{FT})$ and its 
interacting HW transactions $(\mathcal{HT})$ from Figure~\ref{fig:interleaving1}. 
The description above the arrows 
in column 1 shows the events in $\mathcal{FT}$ and the letter below the
arrows denotes the event type, producer $(\mathcal{P})$ or consumer 
$(\mathcal{C})$. Arrows with empty description below denotes reading of interface
variables or local variables in $\mathcal{FT}$.  Arrows with no description
simply denotes control-flow join.  The entries in the right column of
Table~\ref{transaction} shows the corresponding transactions in HW.  We 
denote a transaction in HW module with the name of the module,
transmitter module in UART ($uart\_tx$), receiver module in UART ($uart\_rx$), or
the top UART module ($uart\_top$).
%
\begin{table}
\begin{center}
{
 \scriptsize
\begin{tabular}{|c|c|c|}
\hline
  Firmware & Hardware  \\
  Transaction ($\mathcal{ST}$) & Transaction ($\mathcal{HT}$) \\ 
\cline{1-2}
   $s_1 \xrightarrow[]{irq_o} s_2 \xrightarrow[\mathcal{C}]{inb()} s_4
   \xrightarrow[]{status == 0x0c} s_6 \xrightarrow[\mathcal{P}]{outb()} s_9 \rightarrow
   s_{11} \rightarrow s_{12}$  & $s_2 \xrightarrow[\mathcal{C}]{inb()} s_4\;\; uart\_{rx}$
   \\ 
   & $s_6 \xrightarrow[]{outb()} s_9\;\; uart\_{tx}$ \\  \hline

@@

\textbf{Step 3: Co-verification Model}
%
An unified co-verification model is constructed through appropriate composition of 
FW and its interacting HW threads.  This is done by instrumenting the 
software netlist model of HW RTL inside the FW thread at every invocation 
of the $next\_timeframe()$ primitive in the interface functions.  Recall that a
call to $next\_timeframe()$ is used to advance the HW clock by one cycle. A call
to the software netlist emulates the same effect.  Furthermore, a software
netlist is a sequential model of the HW RTL represented in C.  Thus, the
composition leads to a single-threaded sequential co-verification model in C.  
%
We now formally define a our co-verification model, denoted by 
$\mathcal{M}_{seq}$.
%
\[ 
\begin{array}[t]{@{}lll}
  \mathcal{M}_{seq} & {:}{:}{=} & \mathit{Procedure} \\
\mathit{Procedure} & {:}{:}{=} & \mathit{Statement} \mid \mathit{Procedure} \\
\mathit{Statement} & {:}{:}{=} & CStatement \mid \mathit{moduleName(Var_1,\dots,Var_n)} \\
\mathit{CStatement} & {:}{:}{=} & x {:}{=} exp \mid \mathit{ITE}(b, s_1,s_2) \mid \mathit{s_1;s_2} \mid loop\{s\} \\ 
\end{array}
\]
%
Consider sets of expressions $Exp$ and Boolean expressions $BExp$ 
over variables $Var$ of $\mathcal{M}_{seq}$ such that $(exp \in Exp)$ and 
$(b \in BExp)$. A $\mathit{CStatement}$ is an assignment,
conditional, sequential concatenation or a loop.
$\mathit{moduleName(Var_1,\dots,Var_n)}$ invokes the top level 
procedure of $\mathcal{SN}$, which is also the top level 
module of the HW RTL, since the translation from RTL to software preserves
the module hierarchy.  The interface variables $\{Var\_1,\dots,Var\_n\}$ 
(input, output and inout ports) are declared inside the 
FW to communicate with $\mathcal{SN}$.  Figure~\ref{compose} shows the 
composition of $\mathcal{SN}$ and FW thread for the UART IP.
%

\textbf{Step 4: Property Driven Slicing of Co-verification Model}
A property-driven slicing is performed on the unified model, $\mathcal{M}_{seq}$.  
This step is purely syntactic, meaning that we perform a backward dependency 
analysis starting from the property which only preserve those 
program fragments that are relevant to a given property. The sliced program 
is then passed to the symbolic execution engine for path-based exploration. \\
%
%=======================================================================================
%\subsection{\verifox: Path-wise Symbolic Execution Tool} 
%=======================================================================================
\input{verifox}
%
\subsection{Approach 2: Monolithic Co-verification Technique}
%
\begin{figure}[t]
\begin{center}
\includegraphics[scale=0.6]{figures/traditional_flow.pdf}
\caption{Monolithic HW/SW Co-verification Flow}
\label{fig:conventional}
\end{center}
\end{figure}
%
Figure~\ref{fig:conventional} illustrates the conventional approach to HW/SW
co-veri\-fi\-cation, as implemented in the state-of-the-art co-verification
tool, \hwcbmcv~\cite{CKY03,vlsid13}.  \hwcbmcv is the only open-source
formal co-verification tool that supports Verilog RTL (System Verilog 2009
standard) and C/C++ firmware.  In contrast to our proposed approach,
\hwcbmcv maintains two separate flows for HW and FW.  The top flow in
Figure~\ref{fig:conventional} uses synthesis to obtain either a bit-level or
a word-level netlist from Verilog RTL.  The bottom flow illustrates the
translation of the C program into static single assignment (SSA) form. 
These two flows meet only at the solver.  Thus, \hwcbmcv generates a
monolithic formula from the C and RTL description, which is then checked
with SAT/SMT solvers.  \hwcbmcv provides specific handshake primitives such
as $next\_timeframe()$ and $set\_inputs()$ to model FW-HW communications.
\rmcmt{
To this end, \hwcbmcv constructs a co-verification model through 
in tandem symbolic execution of the HW and FW models.  A bit-level 
netlist representation in And Inverter Graph (AIG) format or word-level netlist in
format similar to SMT-LIB standards is synthesized from a HW Register Transfer 
Level (RTL) implementation. Similarly, the SW, given in C, is automatically 
translated into a Static Single Assignment (SSA) form.  A monolithic verification 
condition is generated from these two models which is then solved using a 
}
%
\Omit{
The hardware and firmware run independently of each other. 
The communication between them takes place through these function calls. 
}
%===============================================================================
\section{Property Specification for Co-verification}\label{property}
%===============================================================================
Lack of support for property specification in a HW/SW co-design is one of the
stumbling blocks for the application of formal techniques in co-verification.  
In this paper, we express a co-design property in C 
with the support of special primitive, called {\em next\_timeframe()}, 
that can express temporal correlation between HW and FW events. 
In this paper, we classify co-design properties into two 
classes -- {\em transaction-level} property and {\em component-level} property.
%-------------------------------------------------------------------------------
\subsection{Transaction-level Property}
%-------------------------------------------------------------------------------
A {\em Transaction-level} property ($\psi_{t}$) formally captures the 
design intent of the interaction between a $\mathcal{ST}$ and $\mathcal{HT}$, 
that is, it is defined at the transaction boundaries.  
Recall that a $\mathcal{ST}$ is a service in response to some external environment 
or HW interrupts (for example acknowledgement or exceptions). Similarly, 
$\mathcal{HT}$ is a finite-length service in response to some SW events or 
other HW events.
